\section{Introduction}\label{cha:introduction}

Random numbers are useful, important, and even critical, prerequisites in many areas.
Lotteries, sport and military drafts, games, and gambling all rely on random numbers.
Cryptographic schemes used in e.g.\ modern communication contain constants that exhibit randomness.
\stefan{this paragraph is nice now. what you could consider however is to add citations here and there (e.g., to cryptographic schemes that need randomness, to lotteries, to ...}
Also in academia, random numbers are required in e.g.\ randomized trials and simulations of unpredictable processes, and in computer science, randomized algorithms are one use case.

Some of these examples happen in a setting where people depend on the outcome of the random draw.
\stefan{I think here you already think about "public randomness", no? your examples look like it and then you talk about NSA. If so, it is fine but then emphasize it (e.g., say "where *multiple* people depend on the randomness of a *public* draw).
If not so, then write this a bit differently: especially in the next paragraph you talk about NSA but if you talk about "trustwhorthy random numbers" more generally there are many other aspects that matter: I need to trust my algorithm, I need to trust my computer, I need to trust ... before we can talk about NSA}
In other words, they have a stake in the value of the random number --- this can for example be a monetary prize, an advantage or disadvantage, or in the case of cryptography, the random number helps guarding confidential information.
Thus, the quality, or integrity, of such number is important.
Essentially, the entity generating the random number should be trustworthy, in the sense that they will not manipulate the outcome to anyone's advantage or disadvantage.
However, trustworthiness is difficult to obtain.
There are numerous examples of traditional lotteries manipulated --- recently, the information security director of the American Multi-State Lottery Association, Eddie Tipton, was charged with installing a rootkit on the computer generating the random numbers, resulting in him winning the \$14.3 million prize~\cite{bbclotteryexploit}.
Another example is from 1980, where the host of lottery television broadcast switched out some of the ping pong balls with slightly heavier ones, resulting in a highly biased draw~\cite{lotteryscandal-666}.

\gls{nsa} leaks in the past decade further aggravates the question of trust.
\stefan{NSA comes out of the blue: maybe start differently: "While trust  is important in case where people depend on the random number, it is not always easy to achieve.  The randomness of a random number may be manipulated in many ways, including powerful attackers sch as the NSA}
Massive manipulation and eavesdropping as well as backdoors to cryptographic encryption schemes were revealed.
So even if the entity generating the random numbers is trusted, other circumstances may degrade the trust.
In any case, having blind faith in an entity is not desirable.
Even though they describe their generation process, we have no proof that a random number is generated as they claim it is.

Imagine using a random number generator that somehow cryptographically signs its output and provides a verifiable proof saying that it was really generated  as they claim.
\stefan{this paragraph is not well integrated in the intro: it is not quite clear what you mean here: please elaborate and integrate better}
In such a case, an entity performing a draw could keep requesting a value until a \enquote{satisfactory} value is found.
This value is signed and has a proof --- but it is still biased.

The solution could be to use a \emph{randomness beacon}.
\stefan{The solution *to the problem of trustworthy randomness" could be to use...?}
Michael Rabin introduced this term in 1983~\cite{rabin1983transaction} to describe a trusted public service that provides fresh randomness at regular intervals.
An entity wishing to use a random number should then:
\begin{eromanate*}
    \item announce a function mapping the beacon output space to their desired space; this desired space could for example be lottery numbers between 1 and 36, and
    \item announce a specific time in the future at which point the beacon output will be used.
\end{eromanate*}
This tactic delegates the trust issue to the randomness beacon.
The entity commits to using a future unknown random number which effectively makes the entity unable to keep requesting values until a satisfactory value is found.
Furthermore, anyone can see the same random value of the beacon and verify the outcome by using the announced mapping (and of course verifying the mapping is fair).

This still leaves the problem of trusting the beacon to not bias the random number.
As an example, the \gls{nist}, in USA, runs a randomness beacon.
To generate the random value, they use a setup that measures quantum mechanical effects.
There is, however, no proof that the value has been generated by the quantum mechanical procedure as they claim.
Users have to blindly trust that the value is generated as described.
Furthermore, the reputation of the \gls{nist} is somewhat tarnished, as they were involved in the publication of the Dual Elliptic Curve PRNG standard, which they now have admitted contained a back door~\cite{nist2014backdoor}.
While there, to our knowledge, exists no known cases where \gls{nist} have biased the outcome, they potentially have the ability to.

Some literature exists on making randomness beacons more trustable, and we find it desirable to investigate such concept of trust.
We have not been able to find extensive research on the topic, but the existing research is promising, and this paper will therefore try to classify these to give an overview of the topic.

\subsection*{Contributions}\label{subsec:contributions}
% comparison parameters
In this paper, we produce a general randomness beacon definition. Afterwards, we create a tangible set of properties which can be used to classify different approaches to creating randomness beacons.
We will be focusing on trust, i.e.\ how a given user of the randomness beacon can trust it, and if they should trust it.
Alongside picking out shortcomings of the different approaches, we will examine where they excel compared to both each other and current solutions for public randomness.

% actual taxonomy
We provide the, to our knowledge, first taxonomy of such implementations accompanied by theoretical solutions and ideas, which seek to improve the trustability of randomness sources.

The rise of cryptocurrencies, and more importantly blockchain technologies, has spurred interest in establishing trust in a setting where participants are mutually distrusting.
Randomness beacons display a similar setting, and thus many approaches utilize the blockchain technology.
As such, blockchain technology will be described briefly and incorporated into the taxonomy of randomness beacons.

\paragraph{The paper is organized as follows:}
In \cref{sec:use_cases_of_randomness_beacons} we describe the real-world context of randomness beacons by showing motivating use cases.
We present preliminaries in \cref{sec:preliminaries}, before diving into randomness beacons in \cref{sec:beacons}.
This section will specify the properties and settings of such beacons, and be the foundation of classifying current randomness beacon approaches.
Furthermore, we define three archetypes of randomness beacons, which loosely describes the prevalent trends in such implementations.
In \cref{sec:classification} we present, discuss, and classify existing approaches alongside non-beacon approaches to generating randomness. 
Lastly, we conclude upon this work in \cref{sec:conclusion}.


% blockchain magic to the rescue
%We also introduce new ways of improving existing solutions, by harnessing the immutability and consensus power of blockchain networks.
