\subsection{Beacon Performance}
One aspect of beacons we have not analysed much is their performance.
In practical use of a beacon, performance is an important parameter to consider.
When considering performance, the output frequency of the beacon is the primary metric we consider.
Depending on the setting, having fresh randomness available frequently could be important for e.g.\ fair contract signing~\cite{rabin1983transaction}.
We briefly mention it in the analysis, but the frequency of a beacon can be correlated to our main archetypes of beacons.
The \emph{autocratic collector} practically dictates their frequency themselves.They are limited only by the speed at which they can collect data, which can be very high.
To exemplify this, the \gls{nist} beacon output strings every 60 seconds~\cite{nistbeacon}.

The \emph{transparent authority} is also limited by their input source, but in their case the limitation is much greater.
They require the source to be published by a third party before they can start their computation, which puts the frequency out of their control.
This is best exemplified with the examples that use the bitcoin blockchain as source~\cite{bonneau2015bitcoin, bentov2016bitcoin, bunz2017proofsof}.
The bitcoin blockchain is designed to produce a new block at a set rate~\cite{nakamoto2008bitcoin}, which currently aims for a new block every 10 minutes.
This frequency may be too low for some usecases, in which case another type of beacon would be preferable.

By contrast, the frequency of \emph{Specialized \gls{mpc}} beacons is completely dependent on the participants.
As the randomness is produced from their inputs, the frequency can be as low or high as the participants decide to set it.

Another performance metric is the initial latency, i.e.\ the time it takes from starting the beacon protocol to the first outcome is produced.
This bootstrapping time is usually insignificant since beacons are intended to be services running for a greater period.
The initial latency is determined by two things:
\begin{enumberate*}
    \item the time it takes to collect input $I_t$, e.g.\ from users or waiting on some external source; and
    \item the time it takes to perform the computation $f(I_t)$.
\end{enumberate*}
Publishing the outcome is not considered in this metric, since the outcome effectively is available as soon as it is computed.
Since the computation time of $f(I_t)$ effects the latency, beacons using delay functions such as \citetalias{bunz2017proofsof} will often have a longer bootstrapping period than beacons with less time-consuming computations such as \citetalias{bentov2016bitcoin}.
